The User Behavior On Online Judge Website

### 2017-04-11 oj.tex
add model

\begin{subfigure}{0.45\textwidth}
\includegraphics[width=0.9\linewidth, height=4cm]{solved-seq1.png} 
\caption{Solved number series}
\label{fig:subim1}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=0.9\linewidth, height=4cm]{solved-seq2.png}
\caption{Log solved number series}
\label{fig:subim2}
\end{subfigure}

@@

There's a baseline regression have been run to

@@

\begin{figure}[h]
\includegraphics[width=0.5\textwidth, inner]{model1-resid.png}
\caption{Plot of residuals of model 1}
\end{figure}

@@

$$
\log(solve_i) = \beta_0 + \beta_1 id_i + \beta_2 diff_i + \epsilon_i
$$

@@

\begin{figure}[h]
\includegraphics[width=0.5\textwidth, inner]{model2-resid.png}
\caption{Plot of residuals of model 2}
\end{figure}

>>>>

\begin{subfigure}{0.45\textwidth}
\includegraphics[width=0.9\linewidth, height=4cm]{solved-seq1.png} 
\caption{Solved number series}
\label{fig:f1}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=0.9\linewidth, height=4cm]{solved-seq2.png}
\caption{Log solved number series}
\label{fig:f2}
\end{subfigure}

@@

There's a regression have been run as baseline.

@@

\begin{figure}[h]
\includegraphics[width=0.5\textwidth, inner]{model1-resid.png}
\caption{Plot of residuals of model 1}
\label{fig:f3}
\end{figure}

@@

The only change of model 2 is that dependent variable $solve$ is transform to $log(solve)$.
$$
\log(solve_i) = \beta_0 + \beta_1 id_i + \beta_2 diff_i + \epsilon_i
$$

@@

\begin{figure}[h]
\includegraphics[width=0.5\textwidth, inner]{model2-resid.png}
\caption{Plot of residuals of model 2}
\label{fig:f4}
\end{figure}

\frametitle{Model 3}

$$
\log(solve_i) = \beta_0 + \beta_1 id_i + \beta_2 diff_mid + \beta_3 + diff_hard + \epsilon_i
$$

\begin{center}
\scalebox{0.5}[0.5]{
\begin{tabular}{lclc}
\toprule
\textbf{Dep. Variable:}    &    log(solve)    & \textbf{  R-squared:         } &     0.907  \\
\textbf{Model:}            &       OLS        & \textbf{  Adj. R-squared:    } &     0.906  \\
\textbf{Method:}           &  Least Squares   & \textbf{  F-statistic:       } &     841.8  \\
\textbf{Date:}             & Tue, 11 Apr 2017 & \textbf{  Prob (F-statistic):} & 6.87e-133  \\
\textbf{Time:}             &     14:38:30     & \textbf{  Log-Likelihood:    } &   -192.36  \\
\textbf{No. Observations:} &         262      & \textbf{  AIC:               } &     392.7  \\
\textbf{Df Residuals:}     &         258      & \textbf{  BIC:               } &     407.0  \\
\textbf{Df Model:}         &           3      & \textbf{                     } &            \\
\textbf{Covariance Type:}  &    nonrobust     & \textbf{                     } &            \\
\bottomrule
\end{tabular}
%\caption{OLS Regression Results}
}
\scalebox{0.5}[0.5]{
\begin{tabular}{lccccc}
\toprule
                           & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
\midrule
\textbf{Intercept}         &      11.2770  &        0.066     &   169.869  &         0.000        &        11.146    11.408       \\
\textbf{diff\_mid[T.True]}  &      -1.0259  &        0.102     &   -10.088  &         0.000        &        -1.226    -0.826       \\
\textbf{diff\_hard[T.True]} &      -0.6194  &        0.092     &    -6.731  &         0.000        &        -0.801    -0.438       \\
\textbf{id}                &      -0.0124  &        0.001     &   -16.695  &         0.000        &        -0.014    -0.011       \\
\bottomrule
\end{tabular}
}
\scalebox{0.5}[0.5]{
\begin{tabular}{lclc}
\toprule
\textbf{Omnibus:}       & 32.712 & \textbf{  Durbin-Watson:     } &    0.774  \\
\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &   45.065  \\
\textbf{Skew:}          &  0.810 & \textbf{  Prob(JB):          } & 1.64e-10  \\
\textbf{Kurtosis:}      &  4.225 & \textbf{  Cond. No.          } &     501.  \\
\bottomrule
\end{tabular}
}
\end{center}

The DW statistic looks better than using $diff$ directly. But if we inspect the the plot of residual of model3, 
the same pattern is weaken while there aren't fundamental change what we expect.

\begin{figure}[h]
\includegraphics[width=0.5\textwidth, inner]{model3-resid.png}
\caption{Plot of residuals of model 3}
\end{figure}

\frametitle{Why the residual pattern occur? The road to user personas. }

Although we can run a segmented regression, but more fundamental origin is interesting to investigate.
A idea to model this phenomenon is to try to decompose user into distinct groups
who act differently in problem solving process.

For example, the "light" user may solve first few problems and then leave while the "hard core" 
user would try solve many problem until their interest wore off and nerd would like to solve prolbem
labeled in hardest. 
These effects are mixed and hard to distinguish if we only consider the infomation given by OJ website.

For example, the number of hit of chinese translation of description of origin problem is a variable relate 
solved number. In fact, we can run a parallel model on hit data.
